Alternating Automata Modulo First Order Theories

### 2019-02-07 quantifiers/body.tex
ok

Consider, for instance the problem of proving that $\lang{A} \subseteq
\lang{B}$, where $A$ and $B$ are the timed automata in
Fig. \ref{fig:ta}. The automaton $A$ ($B$) has a single clock $x$
($y$) which is reset on the transition from $s_1$ to $s_2$ ($q_1$ to
$q_2$). Intuititvely, $A$ recognizes the sequences in which all events
are $a$ and the second event, if it occurs at all, it occurs after at
least $2$ time units. On the other hand, $B$ recognizes the sequences
in which there exists an event $a$ such that no event occurs after it
in exactly $1$ time unit. Formally, $\lang{A} = \set{a, t_1, \ldots a,
  t_n \mid t_1, \ldots, t_n \in \real,~ n > 1 \Rightarrow t_1 \geq 2}$
and $\lang{B} = \set{\sigma_1, t_1 \ldots \sigma_{i-1}, t_{i-1}, a,
  t_i, \ldots \sigma_n, t_n \mid \sigma_1, \ldots, \sigma_n \in
  \set{a,b},~ n \geq 1,~ t_1, \ldots, t_n \in \real,~ 1 < i < n
  \Rightarrow t_i-t_{i-1} \neq 1}$. It is proved\footnote{See
  \cite[Theorem 1]{AlurMadhusudan04} for a proof.}  that $\clang{B}$
cannot be recognized by a timed automaton, thus the inclusion cannot
be proved in the framework of timed regular languages, as $\lang{A}
\cap \clang{B} = \emptyset$.

>>>>

Consider, for instance the problem of proving that $\lang{A} \subseteq
\lang{B}$, where $A$ and $B$ are the timed automata in
Fig. \ref{fig:ta}. The automaton $A$ ($B$) has a single clock $x$
($y$) which is reset on the transition from $s_1$ to $s_2$ ($q_1$ to
$q_2$). Intuititvely, $A$ recognizes the sequences in which all events
are $a$ and the second event, if it occurs at all, it occurs after at
least $2$ time units. On the other hand, $B$ recognizes the sequences
in which there exists an event $a$ such that no event occurs after it
in exactly $1$ time unit. Formally, $\lang{A} = \set{a, t_1, \ldots a,
  t_n \mid t_1, \ldots, t_n \in \real,~ n > 1 \Rightarrow t_2-t_1 \geq
  2}$ and $\lang{B} = \set{\sigma_1, t_1 \ldots \sigma_{i-1}, t_{i-1},
  a, t_i, \sigma_{i+1}, t_{i+1}, \ldots \sigma_n, t_n \mid \sigma_1,
  \ldots, \sigma_n \in \set{a,b},~ n \geq 1,~ t_1, \ldots, t_n \in
  \real,~ 1 \leq i < n \Rightarrow t_{i+1}-t_i \neq 1}$. It is
proved\footnote{See \cite[Theorem 1]{AlurMadhusudan04} for a proof.}
that $\clang{B}$ cannot be recognized by a timed automaton, thus the
inclusion cannot be proved in the framework of timed regular
languages, as $\lang{A} \cap \clang{B} = \emptyset$.
